MSA Asthma Place of Service Timeseries

### 2018-06-14 r_scripts/analysis/msa_asthma_timeseries.Rmd
updated asthma time series.

# function list
compare_df <- outcome_list %>% 
  map_dfr(., function(df){
    df <- outcome_list[[5]]
    serv_pl <- unique(df$service_place)
    serv_pl
    # model
    mod <- glm(n_events ~ 0 + metroarea*month_name + offset(log(pop)), 
                family = poisson, data = df)

    summary(mod)
    contr_msa_jul_to_sep <- rbind(
      #'Bend: Aug to Jul' = c(0,0,0,0,0,0,0,-1,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),
      #'Bend: Aug to Sept' = c(0,0,0,0,0,0,0,0,-1,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),
      #'Cor: Aug to Jul' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,0,0,1,0,0,0,0,0,0,0,0,0),
      #'Cor: Aug to Sept' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,0,0,1,0,0,0,0),
      #'Eug: Aug to Jul' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,0,0,1,0,0,0,0,0,0,0,0),
      #'Eug: Aug to Sept' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,0,0,1,0,0,0),
      'Med: Aug to Jul' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,0,0,1,0,0,0,0,0,0,0),
      'Med: Aug to Sept' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,0,0,1,0,0),
      'Port vs Med: Aug to Jul' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-.5,-.5,0,0,0,.5,.5,0,0,0,0,0,0)
      #'Port: Aug to Sept' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,0,0,1,0),
      #'Sal: Aug to Jul' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,0,0,1,0,0,0,0,0),
      #'Sal: Aug to Sept' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,0,0,1)
      )

>>>>

# function list
compare_df <- outcome_list %>% 
  map_dfr(., function(df){

    serv_pl <- unique(df$service_place)
    serv_pl
    # model
    mod <- glm(n_events ~ 0 + metroarea*month_name + offset(log(pop)), 
                family = poisson, data = df)

    contr_msa_jul_to_sep <- rbind(
      #'Bend: Aug to Jul' = c(0,0,0,0,0,0,0,-1,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),
      #'Bend: Aug to Sept' = c(0,0,0,0,0,0,0,0,-1,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),
      #'Cor: Aug to Jul' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,0,0,1,0,0,0,0,0,0,0,0,0),
      #'Cor: Aug to Sept' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,0,0,1,0,0,0,0),
      #'Eug: Aug to Jul' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,0,0,1,0,0,0,0,0,0,0,0),
      #'Eug: Aug to Sept' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,0,0,1,0,0,0),
      'Med: Aug to Jul' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,0,0,1,0,0,0,0,0,0,0),
      'Med: Aug to Sept' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,0,0,1,0,0),
      'M v B: Aug to Jul' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,1,0,-1,0,0,1,0,0,0,0,0,0,0),
      'M v C: Aug to Jul' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,1,0,0,-1,0,1,0,0,0,0,0,0,0),
      'M v E: Aug to Jul' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,1,0,0,0,-1,1,0,0,0,0,0,0,0),
      'M v P: Aug to Jul' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,1,0,0,0,-1,1,0,0,0,0,0,0),
      'M v S: Aug to Jul' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,1,0,0,-1,0,1,0,0,0,0,0)
      #'Port: Aug to Sept' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,0,0,1,0),
      #'Sal: Aug to Jul' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,0,0,1,0,0,0,0,0),
      #'Sal: Aug to Sept' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,0,0,1)
      )
